
%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

% \usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
% \usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{
		;company; \\
		;address; \\
		;country; }

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{center}
	\large\textbf{Garrett Everding} \\ % Your name
	% \vspace{15pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
 \moveleft\hoffset\vbox{\hrule width\textwidth height 1pt}\smallskip
	137 University Ave. W. \\ 
	Waterloo, ON \\ 
	(226) 868-5820
\end{center} 
% \vfill

\signature{Garrett Everding} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Hiring Manager}
 
Here is why you should hire me. I am a fourth year student at the University of Waterloo in Computer Engineering. This has given me a combined 20 months of real world experience. For 8 of those months I was one of two developers working on a platform to manage a growing electronic record label. For the last year I have been working with a team to build a council whose primary goal is to create programs that encourage a sense of community among blind and partially sighted youth.

I am not your typical intern. I am not someone who spends each and every day writing code. I am the person you should hire if you want someone who will push projects forward because I am passionate about them and because I believe in them. I am a very motivated and dedicated worker and I work well both as a member of a team and on my own.

I am looking to work for a company where I am surrounded by passionate and driven people who want to push what is possible and have fun doing it. I want to find a company that is not afraid to reimagine who they are and what they are doing. I want to work in an environment that fosters creativity and new ideas. I believe that ;company; is this company and that is why I want to work for you.

Regards, \\

Garrett Everding


% \encl{Curriculum vitae, employment form} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}
