% LaTeX resume using res.cls
\documentclass[margin]{res}
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Garrett Everding}
 \moveleft.5\hoffset\centerline{4A Computer Engineering}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{137 University Ave. W}
 \moveleft.5\hoffset\centerline{Waterloo, Ontario}
 \moveleft.5\hoffset\centerline{gseverdi@uwaterloo.ca}
 \moveleft.5\hoffset\centerline{github.com/geverding}
 \moveleft.5\hoffset\centerline{(226) 868-5820}


\begin{resume}

\section{ SKILL\\ SUMMARY }
Strong problem solving and analytical skills\\
Experienced with organizing a multi-discipline and remote team\\
Comfortable in a constantly evolving and fast-paced environment\\
Work well in a group environment and with minimal supervision

\section{TECHNICAL\\PROFICIENCY}
{\sl Languages:} Javascript, Scala, Haskell, C\\
{\sl Platforms:} Linux, OSX\\
{\sl Software:} Vim, Git, \LaTeX\\
{\sl Technologies:} Node.js, Backbone.js, d3.js, MongoDB, MySQL, Redis, AWS

\section{EDUCATION}
{\sl Candidate for Bachelor of Applied Science,} Honours (Coop) Computer Engineering \\
University of Waterloo, Waterloo, Ontario \hfill Sept. 2010 - Present

\section{EXPERIENCE}

{\sl Software Developer} \hfill May 2013 - Aug. 2013 \\
Monstercat, Waterloo, ON.
\begin{itemize}  \itemsep -2pt %reduce space between items
  \item Developed Javascript heavy web applications for managing a record label and a YouTube network
  \item Implemented intuitive controls to streamline data entry and management
  \item Played a key role in architectural decisions to improve functionality and maintainability
  \item Maintained critical production servers
\end{itemize}

{\sl Software Developer} \hfill Sept. 2012 - Dec. 2012 \\
Monstercat, Waterloo, ON.
\begin{itemize}  \itemsep -2pt %reduce space between items
  \item Built real-time, interactive promotional web applications for album releases
  \item Created online face for newly launched sister company (EDM Spotlight)
  \item Implemented fluid and intuitive controls for a new record label management system
  \item Maintained and setup production and development servers for performance driven applications
\end{itemize}

{\sl Software Designer} \hfill Jan. 2012 - April 2012 \\
International Datacasting, Ottawa, ON.
\begin{itemize}  \itemsep -2pt %reduce space between items
  \item Worked closely with the core software developers to implement new software features and fix bugs
  \item Developed for the head-end system, which transmits content files to receivers via satellite and terrestrial links
  \item Implemented new webservice calls for the head-end system to remotely manage customer satellite receivers
  \item Enhanced and fixed bugs in receiver firmware
\end{itemize}

\pagebreak
% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Garrett Everding}
 \moveleft.5\hoffset\centerline{Page 2}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip

{\sl Junior Software Developer} \hfill May 2011 - Aug. 2011 \\
N-Able Technologies, Ottawa, ON.
\begin{itemize} \itemsep -2pt
  \item Improved the performance of code by using a variety of safe Multi-threading techniques
  \item Implemented an cross-platform framework for use on Windows, Linux and OSX systems
  \item Created System Tray to provide basic control over N-Able Agent Software
  %\item Used batch files to automate tasks
\end{itemize}

\section{RELEVANT PROJECTS}

{\sl WikiWalk (http://wikiwalk.herokuapp.com) } \\
Visualization of The Wikipedia Game
\begin{itemize} \itemsep -2pt
  \item Generates a tree of interconnected Wikipedia articles given a user specified seed
  %\item Users can specify the number of links to follow on each page and the depth of the graph
  %\item Subsequent pages are randomly selected from all the links on the parent page
  \item Built for the Sortable \{data\} Hackathon using Node.js, Bootstrap, and d3.js
\end{itemize}

{\sl United (http://united.monstercat.com) } \\
Web Promotion for Monstercat's United Album
\begin{itemize} \itemsep -2pt
  \item Utilized Google's Map API to display users geographical locations around the globe
  \item Featured a real-time, scrolling news feed and constantly updating map
\end{itemize}

%{\sl Operating Systems Lab } %\hfill May  2012 - Present
%\begin{itemize} \itemsep -2pt
  %\item Working in pairs to design and developed Unix system-level programs
  %\item Implemented producer/consumer pattern using multi-process and multithreading techniques
  %\item Creating a custom dynamic memory allocation/deallocation API for the RTX Kernel
  %\item Designed code to run in standard and embedded Unix environments
%\end{itemize}


%{\sl Data Structures \& Algorithms} %\hfill Sept. 2011 - Dec. 2011
%\begin{itemize} \itemsep -2pt
	%\item Created Linked Lists, Stacks, Queues, Deques, Hashtables, Trees, Graphs
	%\item Implemented projects using strict performance and memory requirements
%\end{itemize}

%{\sl Digital Computers Lab} %\hfill Sept. 2011 - Dec. 2011
%\begin{itemize} \itemsep -2pt
  %\item Creating calculator in assembly for the Motorola 68k/Coldfire processor
  %\item Calculator takes input from 2 I/O devices (keyboard \& keypad)
  %\item Preforms addition, subtraction, multiplication and combinations of operations
%\end{itemize}

\section{RELEVANT COURSES}
Compilers, Operating Systems, Computer Networks

\section{PROFESSIONAL DEVELOPMENT} 
{\sl Summer Career Opportunity, Recreation and Education} \hfill July 2010
\begin{itemize} \itemsep -2pt
  \item S.C.O.R.E Program ran by the Canadian National Institute for the Blind
  \item Focused on personal development, team building, leadership and career skills and civic responsibility.
  \item Worked as part of a team to build strengths, actively practicing new skills, achieving goals with others
\end{itemize}

\section{COMMUNITY \\ SERVICE}  
{\sl Co-Chair} \hfill May 2013 - Present\\
CNIB National Youth Council
\begin{itemize}\itemsep -2pt
  \item Working with CNIB and other groups to improve services of young adults across Canada
\end{itemize}

{\sl Assistant Coach} \hfill Nov. 2008 - May 2010\\
Arnprior Amateur Wrestling Club, Arnprior, ON
\begin{itemize}\itemsep -2pt
  \item Planned and ran clinics for children (aged 4-12) to teach them the basics of Olympic freestyle wrestling
  \item Assisted head coach at junior and senior team practices and tournaments
\end{itemize}

\section{EXTRA-CURRICULAR \\ ACTIVITIES}
{\it Mini Sumo Challenge}  \hfill Sept. 2010 - Dec. 2010\\
University of Waterloo Robotics Team, Waterloo, ON
\begin{itemize} \itemsep -2pt
  \item Worked in a group to design and construct a Mini Sumo robot
  \item Soldered components to circuit board and constructed internal electronics and chassis
\end{itemize}

\section{GENERAL\\INTEREST}
Programming (FP/Haskell, Distributed Systems), Reading

\end{resume}
\end{document}

